Decade of Lost Precision: A General Framework For Image Feature Matching Without Geometric Constraints

### 2014-11-27 paper.tex
Added line to support assumption #2

According to the second assumption, feature descriptors behave such that when matched, a true correspondence to a \emph{query feature} will always be closer in distance than any other feature in the query image. For this assumption to be violated either the \emph{query image} contains repeating patterns (violating assumption \#1) or the two images are different enough (i.e.\ taken from very different viewpoints or under different lighting conditions) that the descriptor distance between two unrelated features ends up being closer than the distance between a feature and its true correspondence. In this case \emph{Ratio-Match-Ext} and \emph{Mirror-Match} would discard the match while \emph{Ratio-Match} would still attempt to match the descriptor to a feature in the \emph{target image}. Figure~\ref{fig:no_query} shows how the precision of the nearest neighbor match varies with the ratio of the distance to the closest \emph{target feature} over distance to the closest \emph{query feature}. When this ratio is more than 1 there exists a \emph{query feature} which is better matched than the closest \emph{target feature}. The statistic is gathered over 3024 image pairs featuring 3D objects (see Section~\ref{S:3dobjects}) and the results demonstrate that for the cases where the second assumption is violated and \emph{Ratio-Match} might be advantageous, the nearest neighbor in the target image is less likely to be a correct match. % TODO: Create plot and write more precisely

>>>>

According to the second assumption, feature descriptors behave such that when matched, a true correspondence to a \emph{query feature} will always be closer in distance than any other feature in the query image. For this assumption to be violated either the \emph{query image} contains repeating patterns (violating assumption \#1) or the two images are different enough (i.e.\ taken from very different viewpoints or under different lighting conditions) that the descriptor distance between two unrelated features ends up being closer than the distance between a feature and its true correspondence. In this case \emph{Ratio-Match-Ext} and \emph{Mirror-Match} would discard the match while \emph{Ratio-Match} would still attempt to match the descriptor to a feature in the \emph{target image}.

The empirical results of \emph{Self-Match} in Figure~\ref{fig:all_objects} and Figure~\ref{fig:patches} support the assumption. \emph{Self-Match} discards any match where a feature in the query image is more similar to the query feature, yet the algorithm consistently performs equally well or better than \emph{Ratio-Match} supporting the notion that for most all true correspondences the best match is found in the \emph{target image}. We note that even at high recall rates where we find the more challenging matches, this assumption is still supported by the empirical results with \emph{Self-Match} performing on par with \emph{Ratio-Match}.
